ZCB Pricing

### 2018-07-04 ZCB Pricing .Rmd
Addition of rough implicit method

```{r 5}
# Implicit Method

>>>>

```{r 5}
# Implicit Method
# Implicit Method

implicit <- function(alpha,beta,sigma,r,I,J){
  # I = partition of time interval
  # J = partition of short rate variable

  nr <- length(J) # number of rows based on rate grid points
  nc <- length(I) # number of columns based on number of time grid points

  dr <- J[2] - J[1] #length of each sub-interval across J
  dt <- 1/length(I) #length of each sub-interval across I

  # For each j in J we define the following functions at a fixed time point

  pd <- function(j){
    dt*((alpha-beta*J[j+1])/(2*dr) - (sigma^2)/(2*dr^2))

  pm <- function(j){
    dt*(J[j+1] + 1/dt)
  }

  pu <- function(j){
    -dt*((alpha-beta*J[j+1])/(2*dr) + (sigma^2)/(2*dr^2))

  # Setting up tridiagonal matrix
  Diag <- matrix(0,nrow = nr-1,ncol = nr-1)

  # Filling main diagonal
  for (j in 1:(nr-1)){
    Diag[j,j] <- pm(j)

  # Filling lower diagonal
  for (j in 2:(nr-1)){
    Diag[j,j-1] <- pd(j)
  }

  # Filling upper diagonal
  for (j in 1:(nr-2)){
    Diag[j,j+1] <- pu(j)
  }

  B <- matrix(1,ncol = 1,nrow = nr-1) # The matrix of bond prices at maturity time

  for (i in I){
    C <- matrix(0,ncol = 1, nrow = nr-1) # Another matrix for boundary conditions
    C[nr-1,1] <- (-pu(nr-1))*B[nr-1,1]
    C[1,1] <- -pd(1)
    A <- B + C # Working backwards recursively 
    B <- solve(Diag)%*%A 
  }

  B # Output of bond prices at time 0 for varying rates

R <- implicit(0.08,0.8,0.005,0.05,1:50,seq(0,0.1,0.01))
